Type cones of $\b{g}$-vector fans

### 2019-02-11 thirdPaper/draft/typeConeAssociahedra.tex
Corrected some mistakes in Section 3.

@@

\begin{lemma}\label{lemm::coefficients}
 Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat)\setminus \add(\susp T)$, we have that
 \[
  \lambda_A = \langle \ell_A, x \rangle = \langle x, r_A \rangle.
 \]
\end{lemma}
\begin{proof}
 Let~$B\in \ind(\cat) \setminus \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
 \[
  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_A.
 \]
 The equality~$\lambda_A = \langle x, r_A\rangle$ is proved in a similar way.
\end{proof}

@@

 Assume that (2) holds.  Then, by Lemma~\ref{lemm::coefficients}, we have that
 \[
  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \langle \ell_A, x \rangle + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
 \]
 Thus~$x\in \Ksp(\add(\susp T))$, and (1) holds.

@@

\begin{proposition}
 Assume that~$\ind(\cat)$ is finite.  Then the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop::free-set}, the set is free.  Let~$x\in \ker \b g$.  Consider the element
\[
 z = x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
\]
Then for any~$B\in \ind{\cat}$, we have that
\[
 \langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0, 
\]
where the second equality is obtained by using Lemma~\ref{lemm::bilinear-form}.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.  Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$, we get that~$z=0$.  This finishes the proof.
\pg{We need a lemma saying that g is injective on K(add(susp T))}
\end{proof}

@@

We recall the following results and definition from \cite{DehyKeller,Palu}.

\begin{corollary}
 There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
\end{corollary}

>>>>

Before we can prove Theorem~\ref{theo::relations-g-vecteurs}, we need to recall the following results and definition from \cite{DehyKeller,Palu}.

\begin{corollary}\label{coro::grothendieck-g-vectors}
 There is an isomorphism~$\phi:\Kg(\cat) \to \Ksp(\add(T))$ such that~$\ind_T = \phi\circ \b g$.  In particular,~$\Kg(\cat)$ is a free abelian group generated by the~$[T_i]$.
\end{corollary}

We can now begin the proof of Theorem~\ref{theo::relations-g-vecteurs}

@@

\begin{lemma}\label{lemm::coefficients}
 Let~$x\in \Ksp(\cat)$, and write~\[x=\sum_{A\in \ind(\cat)} \lambda_A [A].\]  Then for any~$A\in\ind(\cat)\setminus \add(\susp T)$, we have that
 \[
  \lambda_A = \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle} = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}.
 \]
\end{lemma}
\begin{proof}
 Let~$B\in \ind(\cat) \setminus \add(\susp T)$.  Applying Lemma~\ref{lemm::bilinear-form}, we get that
 \[
  \langle \ell_B, x \rangle = \langle \ell_B, \sum_{A\in \ind(\cat)} \lambda_A [A] \rangle = \sum_{A\in \ind{\cat}} \lambda_A \langle \ell_B, [A] \rangle = \lambda_B \langle \ell_B, [B] \rangle.
 \]
 The equality~$\lambda_A = \frac{\langle x, r_A \rangle}{\langle A, r_A \rangle}$ is proved in a similar way.
\end{proof}

@@

 Assume that (2) holds.  Then, by Lemma~\ref{lemm::coefficients}, we have that
 \[
  x = \sum_{A\in \ind(\cat)\setminus \add(\susp T)} \frac{\langle \ell_A, x \rangle}{\langle \ell_A, A \rangle}[A] + \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i] = \sum_{i=1}^n \lambda_{\susp T_i} [\susp T_i].
 \]
 Thus~$x\in \Ksp(\add(\susp T))$, and (1) holds.

@@

\begin{proposition}
 Assume that~$\ind(\cat)$ is finite.  Then the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$.  Moreover, for any~$x\in \ker \b g$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop::free-set}, the set is free.  Let~$x\in \ker \b g$.  Consider the element
\[
 z = x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
\]
Then for any~$B\in \ind{\cat}$, we have that
\[
 \langle  z, [B] \rangle = \Big\langle x- \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A, [B] \Big\rangle = \langle x, [B] \rangle - \langle x, [B] \rangle = 0, 
\]
where the second equality is obtained by using Lemma~\ref{lemm::bilinear-form}.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$.  Since~$z\in \ker(\b g)$ and since~$\b g$ is injective on~$\Ksp(\add (\susp T))$ by Corollary~\ref{coro::grothendieck-g-vectors}, we get that~$z=0$.  This finishes the proof.
\end{proof}

@@
